\textbf{NBA Party}

### 2017-04-12 init_model.rnw
Added ESPN player data and associated models.

@@

@@

>>>>

##################################################
### Total Points Allowed
##################################################

@@

##################################################
### musicians per log population
##################################################

@@

##################################################
### ESPN
##################################################

espn <- fread('tmp_data/espn_player_data.csv')
espn[, date := as.Date(date)]
lines[, simple.date := as.Date(date)]
data <- merge(lines, espn, by.x = c('team', 'simple.date'), by.y = c('team', 'date')) ### Careful which obs we keep!

data[, dmeaned.free  := free.made/min - mean(free.made/min), by = list(starters, season)]
data[, dmeaned.three := three.made/min - mean(three.made/min), by = list(starters, season)]
data[, dmeaned.reb   := reb / min - mean(reb / min), by = list(starters, season)]

setnames(data, '+/-', 'pm')

lm(dmeaned.three ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary
lm(dmeaned.reb ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary

### WOW! Earn 1-2 points less per minute on average. (Further condition on player position?)
### Next goal: we should be able to recover our grand mean estimate above. That is, test model efficacy 
### by predicting the number of points a team will score using ex-ante minutes of play-time.
lm(I(as.numeric(pm) / min) ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary
